Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-04 edubots_surveys.Rnw
Revises RQ3 according to @oliatsi suggestions
Also revises and closes #6, no more work is needed here, after excellent work by @noorhanabbas.

WhatsApp is, at least in most Western countries,
the most popular MIM platform used by educators to give assignments'
feedback to students, support course discussions, and provide learning
resources in informal learning settings \cite{panah2020study}.  Moreover, the
use of WhatsApp in higher education could enhance social presence
\cite{tang2017mobile} and foster trust relationships between educators
and students embedded in the social learning process
\cite{gachago2015crossing}.

@@

%Olia - Isn't the following paragraph better fittng for RQ3? What kind interactions do teachers prefer with their students? 
Regarding the social factor of chat groups that teachers use in class, according to Fig. \ref{figure:chatbots_messagingorganization} the vast majority prefer small groups only with the students from the same course. These are more focused groups with specific goals and dedicated to the organization of the course and its tasks, and from the pedagogic point of view seem more appropriate to improve the learning process. Interestingly, about 30\% of teachers consider they should not be part of the chat group. Also, only university teachers find interesting a group with all the students and teachers in their own Faculty or School. The lack of teachers from vocational Education here may be the consequence of using specific language such as "Faculty". Moreover, the fact that many universities and schools already use these groups for administrative and social interaction (e.g. \cite{dibitonto2018chatbot}) might be the reason for the low percentage of teachers that selected this response.

@@

The answer, then, to this research question, is that, in general, teachers do {\em not} want to have interaction with students in a chat group.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RQ4 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

WhatsApp is, at least in most Western countries,
the most popular MIM platform used by educators to give assignments'
feedback to students, support course discussions, and provide learning
resources in informal learning settings \cite{panah2020study}.  Moreover, the
use of WhatsApp in higher education could enhance social presence
\cite{tang2017mobile} and foster trust relationships between educators
and students embedded in the social learning process
\cite{gachago2015crossing}; however, this last paper also reflects the need for
learners to "take ownership of the tool" and the advantages of social learning
in general. At the same time, it also mentions different challenges, among which
the most important is the blurring of social and academic life. Examining these
attitudes will be the objective of RQ3 in this paper.

@@

@@

The answer, then, to this research question, is that, in general, teachers do {\em not} want to have interaction with students in a chat group. To a certain point, this would seem to contradict results by Gachago et al. \cite{gachago2015crossing}, although this might be due to cultural attitudes, or other factors such as the average size of classes. It does confirm, however, that the challenges cited in that study, and possibly others, are an obstacle to the adoption of mobile (and other) instant messaging among the community of surveyed teachers.

%Olia - Isn't the following paragraph better fitting for RQ3? What kind interactions do teachers prefer with their students? 
% Moved here
Regarding the social factor of chat groups that teachers use in class, according to Fig. \ref{figure:chatbots_messagingorganization} the vast majority prefer small groups only with the students from the same course. These are more focused groups with specific goals and dedicated to the organization of the course and its tasks, and from the pedagogic point of view seem more appropriate to improve the learning process. Interestingly, and as a cross-check of the answers above, about 30\% of teachers consider they should not be part of the chat group.
This might seem to contradict the results of the other survey, but in fact, being a result of different surveys, to a certain point affirms the same thing: there is a great amount of teachers that would be against being in a chat group with students. Whether that's a slim majority or not, that's open to debate (and would probably need a more pointed survey focused on this), but what is clear is that forcing teachers to create chat groups with students and participate in them would create a certain amount of resistance.
Also, only university teachers find interesting a group with all the students and teachers in their own Faculty or School. The lack of teachers from vocational education here may be the consequence of using specific language such as "Faculty". Moreover, the fact that many universities and schools already use these groups for administrative and social interaction (e.g. \cite{dibitonto2018chatbot}) might be the reason for the low percentage of teachers that selected this response.
